Comparing software variability across and within fMRI analysis packages

### 2022-01-03 paper/paper.tex
camille comments on abstract

\maketitle
\begin{abstract}
  Variability has been broadly observed in functional MRI analyses as a result
  of software differences
  both between and within analytic tools. However, the
  relationship between within-tool and between-tool software variabilities for a
  given analysis is unclear. We extended a previous comparison of fMRI
  analysis software libraries (namely FSL, AFNI, and SPM) and related the
  observed differences to within-tool software variability
  simulated using Monte-Carlo arithmetic. In group analyses, we found that
  between-tool software variability was consistently larger than within-tool software
  variability simulated at the magnitude of
  machine error. In subject analyses, the same within-tool software variability
  approached between-tool software variability in some regions for some subjects.
  Interestingly, within- and between-tool software variabilities appeared moderately
  correlated ($r > 0.5$) in all tested conditions. 
  % Finally, we found that
  % within-tool software variability had effects of similar magnitude to between-tool
  % software variability when simulated from numerical perturbations introduced at the virtual
  % precision of 17 bits --- a high but plausible level of uncertainty for
  % scientific computing libraries. \tristan{Revise from latest results}
  % %  \gk{What does this mean? They only have
  % precision of 17, or they use data that is 17 bits?}
  %  \yohan{agree with Greg, it is unclear and a strong assertion!}
  %  \camille{It is not entirely clear to me how this relates to the previous
  %  conclusions that BT variability was consistently larger than machine
  %  error} \tristan{Better?}
   Our findings motivate the
  continued investigation of within-tool software variability in neuroimaging, and position it
  as a possible proxy for studying some of the arbitrary between-tool software variations.
\end{abstract}

>>>>

\maketitle
\begin{abstract}
  Variability has been broadly observed in functional MRI analyses as a result
  of software differences
  both between and within analytic tools. However, the
  relationship between within-tool and between-tool software variabilities for a
  given analysis is unclear \camille{early on in the abstract, I think that it would be worth specifying what within-tool covers in the context of this paper: i.e. a focus on variations that can be induced by low level libraries as seen for example when using different operating systems -- which is different from within-tool variability that could be induced when using different parameters (e.g smoothing 6mm or 8mm) or algorithms (e.g. FLIRT versus FNIRT in FSL) within the same software } . We extended a previous comparison of fMRI
  analysis software libraries (namely FSL, AFNI, and SPM) and related the
  observed differences to within-tool software variability
  simulated using Monte-Carlo arithmetic. In group analyses, we found that
  between-tool software variability was consistently larger than within-tool software
  variability simulated at the magnitude of
  machine error. In subject analyses, the same within-tool software variability
  approached between-tool software variability in some regions for some subjects.
  Interestingly, within- and between-tool software variabilities appeared moderately
  correlated ($r > 0.5$) \camille{maybe add ``across voxels or across xxx'' so that we understand what the correlation is measuring a bit better?} in all tested conditions . 
  % Finally, we found that
  % within-tool software variability had effects of similar magnitude to between-tool
  % software variability when simulated from numerical perturbations introduced at the virtual
  % precision of 17 bits --- a high but plausible level of uncertainty for
  % scientific computing libraries. \tristan{Revise from latest results}
  % %  \gk{What does this mean? They only have
  % precision of 17, or they use data that is 17 bits?}
  %  \yohan{agree with Greg, it is unclear and a strong assertion!}
  %  \camille{It is not entirely clear to me how this relates to the previous
  %  conclusions that BT variability was consistently larger than machine
  %  error} \tristan{Better?}
   Our findings motivate the
  continued investigation of within-tool software variability in neuroimaging, and position it
  as a possible proxy for studying some of the arbitrary between-tool software variations. \camille{should we add ``for subject-level analyses'' here? Since we said earlier that within-tool was consistently smaller than between tool variability for group studies.}
\end{abstract}
